Visual Search and Pre-crastination

### 2023-10-10 analysis/3_exploratory.Rmd
Swapping factor levels for final plot
self report and beads data

```{r, message=FALSE}
# attach packages
library(rethinking)
library(tidyverse)
library(patchwork)

@@

@@

# Calculate Correlations

@@

dps <- dat %>% filter(pre_crastinate != "intermediate")

@@

  d_out <- tibble(measure = measure,
                  lower = c(r$conf.int[[1]], d$conf.int[[1]]),
                  upper = c(r$conf.int[[2]], d$conf.int[[2]]),
                  feature = c("search", "pre-crastination"))
  return(d_out)
}

@@

dr$col <- as_factor(rep(c(1,1,1,1,2,2,2,2,2,3), each = 2))

@@

>>>>

```{r, message=FALSE}
# attach packages
library(rethinking)
library(tidyverse)
library(patchwork)
library(corrplot)
```

@@

our_cols <- c("#1b9e77", "#7570b3")
options(ggplot2.discrete.fill = our_cols ,
        ggplot2.discrete.colour = our_cols)
```

@@

# Guessing beads

```{r}
dat %>% filter(is.finite(n_beads)) -> dat_beads

ggplot(dat_beads, aes(n_beads)) + geom_histogram(binwidth = 1) +
  scale_x_continuous("number beads sampled", breaks = 1:10)

xlab <- tibble(black = c(0,0,0,1,1,1,1,1,2,2),
               orange= c(1,2,3,3,4,5,6,7,7,8),
               probA = 0.8^black * 0.2^orange,
               probB = 0.2^black * 0.8^orange,
               llr = probB / probA)

ggplot(dat_beads, aes(n_beads)) + geom_histogram(binwidth = 1) +
  scale_x_continuous("llh ratio", breaks = 1:10, labels = xlab$llr)
```
## Link with pre-crastination

```{r}
ggplot(dat_beads, aes(pre_crastinate, n_beads, fill = pre_crastinate)) + 
         geom_boxplot(alpha = 0.5) + 
  scale_y_continuous("number beads sampled") +
  theme(legend.position = "none")
```

## Link with visual search strategey

```{r}
ggplot(dat_beads, aes(as_factor(n_beads), prop_hard)) + 
         geom_boxplot(alpha = 0.5, fill = "purple") +
  scale_x_discrete("number beads sampled") +
  scale_y_continuous("visual search strategy")
```

# Calculate Personality Correlations

## With Our Measures

@@

dps <- dat %>% filter(pre_crastinate != "intermediate") %>%
  mutate(pre_crastinate = fct_drop(pre_crastinate),
         pre_crastinate = fct_relevel(pre_crastinate, "yes"))

@@

  r_beads <- cor.test(dat$n_beads, dat[[measure]])

  d_out <- tibble(measure = measure,
                  lower = c(r$conf.int[[1]], d$conf.int[[1]], r_beads$conf.int[[1]]),
                  upper = c(r$conf.int[[2]], d$conf.int[[2]], r_beads$conf.int[[2]]),
                  feature = c("search", "pre-crastination", "beads"))
  return(d_out)
}

@@

dr$col <- as_factor(rep(c(1,1,1,1,2,2,2,2,2,3), each = 3))

@@

## With themselves

```{r, fig.height=12}

dat %>% select(-person, -site, -targ_side_rel, -bead_colour, -pre_crastinate,
               -prop_hard, -median_rt, -accuracy, -n_pc, -n_beads) %>%
  na.omit -> dat_c

m <- cor(dat_c)
corrplot(m, method = "number")
```

# Self-Report

First, get relevant data:

```{r}
dat %>% select(person, Vsearch_YesNo, prop_hard, Bucket_YesNo, pre_crastinate) %>%
  mutate(Vsearch_YesNo = factor(Vsearch_YesNo, labels = c("no", "yes")),
         Bucket_YesNo = factor(Bucket_YesNo, labels = c("no", "yes"))) %>%
  na.omit() -> dat_sr

## Visual Search

```{r}

ggplot(dat_sr, aes(Vsearch_YesNo, prop_hard, fill = Vsearch_YesNo)) + geom_boxplot(alpha = 0.5)

t.test(filter(dat_sr, Vsearch_YesNo == "no")$prop_hard, filter(dat_sr, Vsearch_YesNo == "yes")$prop_hard)

t.test(filter(dat_sr, pre_crastinate == "no")$prop_hard, filter(dat_sr, pre_crastinate == "yes")$prop_hard)
```

## Buckets

```{r}

dat_sr %>% group_by(Bucket_YesNo, pre_crastinate) %>%
  summarise(n = n()) %>%
  ggplot(aes(pre_crastinate, n, fill = Bucket_YesNo )) + 
  geom_col(position = position_dodge(), alpha = 0.5) +
  scale_fill_discrete("Self-report strategy?")

chisq.test(dat_sr$Bucket_YesNo, dat_sr$pre_crastinate)
